Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-29 cbm-rbd-paper.tex
switch to total cost rate & thresh = 0.1

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{booktabs}
\usepackage{tikz}

@@

Conditional on the realization $\tsysnow > \tnow$ of $\Tsysnow$, the unit cost rate is 
\begin{align}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau               & \text{if } \tsysnow \ge \tnow + \tau \\
c_u / (\tsysnow - \tnow) & \text{if } \tnow < \tsysnow  <  \tnow + \tau \,.
\end{cases}
\label{eq:gtau}
\end{align}
Note that here, $\tau$ is a time span starting from $\tnow$,
and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
where $0$ corresponds to the time of system start-up.
Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] \nonumber\\ 
            &= \frac{c_p}{\tau} \Rsysnow(\tnow + \tau) + c_u \int_0^\tau \frac{1}{\theta} \fsysnow(\tnow + \theta) \dd \theta\,,
\label{eq:gtnowtau}
\end{align}
and $\tausnow = \arg\min \gnow(\tau)$.
Thus $\tausnow$, the optimal moment of maintenance as of $\tnow$,
incorporates all that is known at current time $\tnow$.
%The lower index $\tnow$ of $\tausnow$ emphasizes that
%depends on $\tnow$, and also on the history of the system.
Figure~\ref{fig:ghist1fig2} shows $\Rsysnow(t)$ and the corresponding $\gnow(\tau)$ for a number of current times $\tnow$
in a numeric example which is described in more detail in Section~\ref{sec:examples}.
%illustrates the derivation of $\tausnow$ .

\begin{figure}
\includegraphics[width=\textwidth]{ghist1fig2}
\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
for the system depicted in Figure~\ref{fig:brakesys-layout}
and prior component models as given in Table~\ref{tab:priorparams},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and costs $c_u = 1$, $c_p = 0.2$.}
\label{fig:ghist1fig2}
\end{figure}

@@

Minimizing $\gnow(\tau)$ leads to $\tausnow$,
the optimal moment of maintenance on a prospective time scale.
The minimal prospective unit cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
i.e., for what happens beyond current time $\tnow$.
%$\gstarnow$ increases over time since 
Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
This gives the expected unit cost rate calculated over the full time since system start-up,
under the assumption that maintenance is scheduled for $\tstarnow := \tnow + \tausnow$.
$\gtotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
However, when many (or few but critical) components fail, $\gtotalnow$ may increase,
since then, system failure becomes much more likely, leading to a higher $\gstarnow$.
Figure~\ref{fig:tauhist1fig2} illustrates these relations in the scenario depicted in Figure~\ref{fig:ghist1fig2}.

@@

\begin{figure}
\includegraphics[width=\textwidth]{tauhist1fig2}
\caption{$\tausnow$, $\tstarnow = \tnow + \tausnow$, $\gstarnow = \gnow(\tausnow)$,
and the total unit cost rate $\gtotalnow$ as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
%$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
$\tausnow$ (top left panel) first decreases, then starts to increase during failure-free periods,
dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
If $\tthresh = 1$, the drop of $\tausnow$ from $1.43$ to $0.91$ at $\tnow = 4$ would trigger a maintenance action
at (absolute) time $5$.
Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
the cost-optimal moment of maintenance on the absolute timescale (top right panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
showing that as time progresses, accumulated information indicates that maintenance can be postponed.
Note that $\gstarnow$ (lower left panel) is the momentary cost rate relating to the expected residual lifetime,
differing from the overall cost rate $\gtotalnow$ (lower right panel).
%For the maintenance action triggered at $\tnow = 8$,
%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
At $\tnow = 4$, the overall expected cost rate for repair scheduled at time $4.91$ is $0.064$,
up from $0.055$ for repair scheduled at time $5.33$, as cost-optimal at time $\tnow = 3.9$.}
\label{fig:tauhist1fig2}
\end{figure}

@@

Here, we illustrate our procedure under three different exemplary failure time histories.
(A more systematic simulation study is then presented in Section~\ref{sec:sim}.)

In the first failure history, we observe
$P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$ and $H = 8$,
and in following the system until $\tnow = 8$,
all other failure times are right-censored.
This is the failure history already used for Figures~\ref{fig:ghist1fig2} and \ref{fig:tauhist1fig2}.
Here, failures observed for type $C$ are thus considerably later than expected,
while for type $P$, the two observed failures are close to the assumed MTTF. 
Both failure at time $8$ for $H$ and non-failure by time $8$ for $M$ are nothing unusual.
In total, due to the late type $C$ failures, prior assumptions turn out to be somewhat pessimistic.
This is reflected in Figure~\ref{fig:tauhist1fig2},
where $\tausnow$ first decreases but then tends to increase during failure-free periods,
which is a consequence of adjusting prior expectations for type $C$ components
due to their unexpected reliability.

***move some text from figure~\ref{fig:tauhist1fig2} caption to here?***

\begin{figure}
\includegraphics[width=\textwidth]{tauhist1fig3}
\caption{Illustration of the gains due to the parameter update at each $\tnow$,
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.
$\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
same with $\tstarnow$ (top right panel).
This is because the adaptive algorithm recognizes that system components are more reliable than expected,
leading to lower current (lower left panel) and total (lower right panels) expected unit cost rates.}
\label{fig:tauhist1fig3}
\end{figure}

The effect of this continuous parameter update is illustrated in Figure~\ref{fig:tauhist1fig3}.
There, the results as seen already in Figure~\ref{fig:tauhist1fig2} are compared
to the case when component parameters are not updated,
while still accounting for the fact that components age,
and that a failed component changes the system layout.
%***so dynamic but not adaptive?***
We see that $\tausnow$ is steadily decreasing in the no update case,
with the jumps at component failure times being less pronounced than in the update case.
Without the continuous update, residual system lifetime continues to be underestimated,
and maintenance is scheduled too early,
leading to lower prospective ($\gstarnow$) and total ($\gtotalnow$) expected unit cost rates.

In a second failure history, we observe the failure times $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$,
and follow the system until $\tnow = 2$ only.
Here, components of type $C$ behave more or less as expected,
while type $P$ components fail quite early.
Overall, prior assumptions are reasonably in line with observed failure behaviour.
%with a slight tendency to earlier failures.
Consequently, the difference between the continuous update case and the no update case is small,
as visualized in Figure~\ref{fig:tauhist2fig3}.
$\tausnow$ values are slightly lower when component parameters are updated,
reflecting the slightly too early failures of type $P$ components.
Due to recommending maintenance to be carried out a bit earlier,
prospective and total cost rate are slightly higher than in the no update case.
However, these differences are minuscule in comparison to the gains offered by the continuous update
in case of the first failure history
(note the differing vertical and horizontal scales in Figures~\ref{fig:tauhist1fig3} and \ref{fig:tauhist2fig3}).

\begin{figure}
\includegraphics[width=\textwidth]{tauhist2fig3}
\caption{Effect of the continuous parameter update for the second failure history ($C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$),
containing slightly early failures of type $P$ components.
With observed failure behaviour more or less in line with expectations,
the model with and without continuous update perform similarly,
unlike in case of the first failure history as depicted in Figure~\ref{fig:tauhist1fig3},
where updating gave considerable gains.}
\label{fig:tauhist2fig3}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=\textwidth]{tauhist4fig3}
\caption{Effect of the continuous parameter update for the third failure history,
containing very early failures ($C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$).}
\label{fig:tauhist4fig3}
\end{figure}

@@

\iffalse
Case 1: failure behaviour as expected,
failure times simulated using Weibull scale parameters $\lambda_k = \ykz$ from Table~\ref{tab:priorparams}.

\begin{figure}
\includegraphics[width=\textwidth]{br1sim1fig5}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated according to prior parameters.}
\label{fig:br1sim1fig5}
\end{figure}

Case 2: failures earlier than expected,
failure times simulated using
$\lambda_k = 0.5 \ykz$ (Figure~\ref{fig:br1sim2fig5}) or
$\lambda_k = 0.2 \ykz$ (Figure~\ref{fig:br1sim4fig5}).

\begin{figure}
\includegraphics[width=\textwidth]{br1sim2fig5}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being earlier ($0.5 \times$ MTTF) than expected.}
\label{fig:br1sim2fig5}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{br1sim4fig5}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being much earlier ($0.2 \times$ MTTF) than expected.}
\label{fig:br1sim4fig5}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{br1sim3fig5}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being later ($2 \times$ MTTF) than expected.}
\label{fig:br1sim3fig5}
\end{figure}
\fi

\begin{figure}
\includegraphics[width=0.5\textwidth]{br1sim1fig5}
\includegraphics[width=0.5\textwidth]{br1sim2fig5}
\includegraphics[width=0.5\textwidth]{br1sim3fig5}
\includegraphics[width=0.5\textwidth]{br1sim4fig5}
\caption{***Simulation study with ***prospective costrate criterion***, $\tthresh = 0.5$.
TL: $\lambda_k =     \ykz$,
TR: $\lambda_k = 0.5 \ykz$,
BL: $\lambda_k = 2   \ykz$,
BR: $\lambda_k = 0.2 \ykz$}
\label{fig:simprospcostrate05}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt01}
\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt02}
\caption{***Simulation study with ***total costrate criterion***, early failures ($0.5 \times$ MTTF),
$\tthresh = 0.1$ (left) and $\tthresh = 0.2$ (right).}
\label{fig:simtotalcostrate0102}
\end{figure}

>>>>

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{sidecap}

@@

*** change to total cost rate

Conditional on the realization $\tsysnow > \tnow$ of $\Tsysnow$, the unit cost rate is 
\begin{align}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau               & \text{if } \tsysnow \ge \tnow + \tau \\
c_u / (\tsysnow - \tnow) & \text{if } \tnow < \tsysnow  <  \tnow + \tau \,.
\end{cases}
\label{eq:gtau}
\end{align}
Note that here, $\tau$ is a time span starting from $\tnow$,
and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
where $0$ corresponds to the time of system start-up.
Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being***
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] \nonumber\\ 
            &= \frac{c_p}{\tau} \Rsysnow(\tnow + \tau) + c_u \int_0^\tau \frac{1}{\theta} \fsysnow(\tnow + \theta) \dd \theta\,,
\label{eq:gtnowtau}
\end{align}
and $\tausnow = \arg\min \gnow(\tau)$.
Thus $\tausnow$, the optimal moment of maintenance as of $\tnow$,
incorporates all that is known at current time $\tnow$.
%The lower index $\tnow$ of $\tausnow$ emphasizes that
%depends on $\tnow$, and also on the history of the system.
Figure~\ref{fig:ghist1fig2T} shows $\Rsysnow(t)$ and the corresponding $\gnow(\tau)$ for a number of current times $\tnow$
in a numeric example which is described in more detail in Section~\ref{sec:examples}.
%illustrates the derivation of $\tausnow$ .

\begin{figure}
\includegraphics[width=\textwidth]{ghist1fig2T}
\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
for the system depicted in Figure~\ref{fig:brakesys-layout}
and prior component models as given in Table~\ref{tab:priorparams},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and costs $c_u = 1$, $c_p = 0.2$.}
\label{fig:ghist1fig2T}
\end{figure}

@@

Minimizing $\gnow(\tau)$ leads to $\tausnow$,
the optimal moment of maintenance on a prospective time scale.
The minimal ***prospective unit cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
i.e., for what happens beyond current time $\tnow$.
%$\gstarnow$ increases over time since 
***Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
This gives the expected unit cost rate calculated over the full time since system start-up,
under the assumption that maintenance is scheduled for $\tstarnow := \tnow + \tausnow$.
$\gtotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
However, when many (or few but critical) components fail, $\gtotalnow$ may increase,
since then, system failure becomes much more likely, leading to a higher $\gstarnow$.
Figure~\ref{fig:tauhist1fig2} illustrates these relations in the scenario depicted in Figure~\ref{fig:ghist1fig2T}.

@@

\begin{SCfigure}
\centering
\includegraphics[width=0.5\textwidth]{tauhist1fig2T}
\caption[t]{$\tausnow$, $\tstarnow = \tnow + \tausnow$ and $\gstarnow = \gnow(\tausnow)$
%and the total unit cost rate $\gtotalnow$ as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
%$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
***$\tausnow$ (left panel) first decreases, then starts to increase during failure-free periods,
dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
If $\tthresh = 1$, the drop of $\tausnow$ from $1.43$ to $0.91$ at $\tnow = 4$ would trigger a maintenance action
at (absolute) time $5$.
Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
the cost-optimal moment of maintenance on the absolute timescale (top right panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
showing that as time progresses, accumulated information indicates that maintenance can be postponed.
Note that $\gstarnow$ (lower left panel) is the momentary cost rate relating to the expected residual lifetime,
differing from the overall cost rate $\gtotalnow$ (lower right panel).
%For the maintenance action triggered at $\tnow = 8$,
%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
At $\tnow = 4$, the overall expected cost rate for repair scheduled at time $4.91$ is $0.064$,
up from $0.055$ for repair scheduled at time $5.33$, as cost-optimal at time $\tnow = 3.9$.}
\label{fig:tauhist1fig2T}
\end{SCfigure}

@@

Below, we illustrate our procedure under three different exemplary failure time histories;
a more systematic simulation study is subsequently presented in Section~\ref{sec:sim}.

In the first failure history, we observe
$P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$ and $H = 8$,
and in following the system until $\tnow = 8$,
all other failure times are right-censored.
This is the failure history already used for Figures~\ref{fig:ghist1fig2T} and \ref{fig:tauhist1fig2T}.
Here, failures observed for type $C$ are thus considerably later than expected,
while for type $P$, the two observed failures are close to the assumed MTTF. 
Both failure at time $8$ for $H$ and non-failure by time $8$ for $M$ are nothing unusual.
In total, due to the late type $C$ failures, prior assumptions turn out to be somewhat pessimistic.
This is reflected in Figure~\ref{fig:tauhist1fig2T},
where $\tausnow$ first decreases but then tends to increase during failure-free periods,
which is a consequence of adjusting prior expectations for type $C$ components
due to their unexpected reliability.

***move some text from figure~\ref{fig:tauhist1fig2T} caption to here?***

\begin{figure}
\includegraphics[width=\textwidth]{tauhist1fig3T}
\caption{Illustration of the gains due to the parameter update at each $\tnow$,
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.
$\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
same with $\tstarnow$ (top right panel).
This is because the adaptive algorithm recognizes that system components are more reliable than expected,
***leading to lower current (lower left panel) and total (lower right panels) expected unit cost rates.}
\label{fig:tauhist1fig3T}
\end{figure}

The effect of this continuous parameter update is illustrated in Figure~\ref{fig:tauhist1fig3T}.
There, the results as seen already in Figure~\ref{fig:tauhist1fig2T} are compared
to the case when component parameters are not updated,
while still accounting for the fact that components age,
and that a failed component changes the system layout.
%***so dynamic but not adaptive?***
***We see that $\tausnow$ is steadily decreasing in the no update case,
with the jumps at component failure times being less pronounced than in the update case.
Without the continuous update, residual system lifetime continues to be underestimated,
and maintenance is scheduled too early,
leading to lower prospective ($\gstarnow$) and total ($\gtotalnow$) expected unit cost rates.

In a second failure history, we observe the failure times $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$,
and follow the system until $\tnow = 2$ only.
Here, components of type $C$ behave more or less as expected,
while type $P$ components fail quite early.
Overall, prior assumptions are reasonably in line with observed failure behaviour.
%with a slight tendency to earlier failures.
Consequently, the difference between the continuous update case and the no update case is small,
as visualized in Figure~\ref{fig:tauhist2fig3T}.
***$\tausnow$ values are slightly lower when component parameters are updated,
reflecting the slightly too early failures of type $P$ components.
Due to recommending maintenance to be carried out a bit earlier,
prospective and total cost rate are slightly higher than in the no update case.
However, these differences are minuscule in comparison to the gains offered by the continuous update
in case of the first failure history
(note the differing vertical and horizontal scales in Figures~\ref{fig:tauhist1fig3T} and \ref{fig:tauhist2fig3T}).

\begin{figure}
\includegraphics[width=\textwidth]{tauhist2fig3T}
\caption{Effect of the continuous parameter update for the second failure history ($C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$)
which is more or less in line with expectations.
%containing slightly early failures of type $P$ components.
***With observed failure behaviour more or less in line with expectations,
the model with and without continuous update perform similarly,
unlike in case of the first failure history as depicted in Figure~\ref{fig:tauhist1fig3T},
where updating gave considerable gains.}
\label{fig:tauhist2fig3T}
\end{figure}

@@

***see Figure~\ref{fig:tauhist4fig3T}

@@

\begin{figure}
\includegraphics[width=\textwidth]{tauhist4fig3T}
\caption{Effect of the continuous parameter update for the third failure history,
containing very early failures ($C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$).
***more }
\label{fig:tauhist4fig3T}
\end{figure}

@@

Case 1: failure behaviour as expected,
failure times simulated using Weibull scale parameters $\lambda_k = \ykz$ from Table~\ref{tab:priorparams}.

\begin{figure}
\includegraphics[width=\textwidth]{br1sim1fig5Tt01}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated according to prior parameters.}
\label{fig:br1sim1fig5Tt01}
\end{figure}

Case 2: failures earlier than expected,
failure times simulated using
$\lambda_k = 0.5 \ykz$ (Figure~\ref{fig:br1sim2fig5Tt01})

\begin{figure}
\includegraphics[width=\textwidth]{br1sim2fig5Tt01}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being earlier ($0.5 \times$ MTTF) than expected.}
\label{fig:br1sim2fig5Tt01}
\end{figure}

@@

\begin{figure}
%\includegraphics[width=\textwidth]{br1sim3fig5Tt01}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being later ($2 \times$ MTTF) than expected.}
\label{fig:br1sim3fig5Tt01}
\end{figure}

% ------------- overview figures ----------------------------------
\iffalse
\begin{figure}
\includegraphics[width=0.5\textwidth]{br1sim1fig5}
\includegraphics[width=0.5\textwidth]{br1sim2fig5}
\includegraphics[width=0.5\textwidth]{br1sim3fig5}
\includegraphics[width=0.5\textwidth]{br1sim4fig5}
\caption{***Simulation study with ***prospective costrate criterion***, $\tthresh = 0.5$.
TL: $\lambda_k =     \ykz$,
TR: $\lambda_k = 0.5 \ykz$,
BL: $\lambda_k = 2   \ykz$,
BR: $\lambda_k = 0.2 \ykz$}
\label{fig:simprospcostrate05}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt01}
\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt02}
\caption{***Simulation study with ***total costrate criterion***, early failures ($0.5 \times$ MTTF),
$\tthresh = 0.1$ (left) and $\tthresh = 0.2$ (right).}
\label{fig:simtotalcostrate0102}
\end{figure}
\fi
